Machine Learning and Mixed Strategy Games

### 2020-12-17 LaTeX/paper.tex
o

% @Author: UnsignedByte
% @Date:   11:12:32, 08-Dec-2020
% @Last Modified by:   UnsignedByte
% @Last Modified time: 00:09:16, 17-Dec-2020

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {./images/} {../results/} }
\usepackage[%  
    colorlinks=true,
    pdfborder={0 0 0},
    linkcolor=blue
]{hyperref}
\begin{document}
\begin{titlepage}
	\vspace*{\stretch{1.0}}
	\begin{center}
		\Large\textbf{Machine Learning and Mixed Strategy Games}\\
		\large\textit{Edmund Lam, Avi Patni}
	\end{center}
	\vspace*{\stretch{2.0}}
\end{titlepage}

\section{Introduction}
\subsection{Mixed Strategy Games}
\label{subsection:MSG}
A Mixed Strategy Game within this paper refers to a subset of strategic games within game theory. A game is defined to have $P$ players and $M$ moves per player. Each player can play any one of their $M$ moves every round, and scores for each player are calculated by accessing the payoff matrix with the results of all their opponents. The payoff matrix is represented by a $P$-dimensional hypercube matrix with side length $M$. Players can be conceptualized as being arranged in a circle, each player is the first in their perspective, which increments for player to their right. Thus, player $P_i$'s' $(1\leq i\leq P)$ score is calculated by accessing the payoff matrix with the coordinates $(P_i, P_{i+1}, \cdots , P_P, P_1, P_2, \cdots , P_{i-1})$. Figure \ref{fig:1} shows an example of how payoffs could be calculated for each player. Players $1$ and $2$ make moves $P_1$ and $P_2$, respectively. Thus, the players will recieve scores $M_{<1,2>}=3$ and $M_{<2,1>}=3$, respectively.

\begin{figure}[h]
  	\begin{align*}
  	&\text{Payoff Matrix} &(P_1&,P_2) &\text{Payoffs}\\
	  &M=
	  \begin{bmatrix}
		  2 & 1\\
		  3 & 0
	  \end{bmatrix}
	  &(1&,2)
	  &(1,3)
	  \end{align*}
  \label{fig:1}
  \caption{Example $2\times2$ payoff matrix with sample moves and resulting scores.}
\end{figure}

@@

\subsection{Prisoner's Dilemma}
\begin{figure}[h]
	\centering\includegraphics[width=4in]{1607068848885-completed/scores.png}
  \caption{Result graphs from test matrix 1.}
  \label{fig:1607068848885-graphs}
\end{figure}

@@

\begin{figure}[h]
	\[\begin{array}{l r|l}
		&\text{Memory Input} & \text{Move Probabilities} \\
		\hline
		1&{[1, 1, 1, 1, 1, 1]} & {[0.937, 0.063]} \\
		2&{[0, 0, 0, 0, 0, 0]} & {[0.015, 0.985]} \\
		3&{[1, 1, 1, 1, 1, 2]} & {[0.999, 0.001]} \\
		4&{[1, 2, 1, 2, 1, 2]} & {[1.000, 0.000]} \\
		5&{[1, 1, 1, 1, 2, 1]} & {[0.104, 0.896]} \\
		6&{[2, 2, 2, 2, 2, 2]} & {[0.048, 0.952]} \\
	\end{array}\]
  \caption{Test cases for first dataset with memories and probability information.}
  \label{fig:1607068848885-cases}
\end{figure}

>>>>

% @Author: UnsignedByte
% @Date:   11:12:32, 08-Dec-2020
% @Last Modified by:   UnsignedByte
% @Last Modified time: 00:56:48, 17-Dec-2020

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {./images/} {../results/} }
\usepackage[%  
    colorlinks=true,
    pdfborder={0 0 0},
    linkcolor=black
]{hyperref}
\title{Machine Learning and Mixed Strategy Games}
\author{
	Edmund Lam \\
	\and
	Avi Patni
}
\begin{document}

\maketitle

\tableofcontents

\section{Introduction}
All source code for this project is public on \href{https://github.com/UnsignedByte/MLMS}{Github}.
\subsection{Mixed Strategy Games}
\label{subsection:MSG}
A Mixed Strategy Game within this paper refers to a subset of strategic games within game theory. A game is defined to have $P$ players and $M$ moves per player. Each player can play any one of their $M$ moves every round, and scores for each player are calculated by accessing the payoff matrix with the results of all their opponents. The payoff matrix is represented by a $P$-dimensional hypercube matrix with side length $M$. Players can be conceptualized as being arranged in a circle, each player is the first in their perspective, which increments for player to their right. Thus, player $P_i$'s' $(1\leq i\leq P)$ score is calculated by accessing the payoff matrix with the coordinates $(P_i, P_{i+1}, \cdots , P_P, P_1, P_2, \cdots , P_{i-1})$. Figure \ref{fig:1} shows an example of how payoffs could be calculated for each player. Players $1$ and $2$ make moves $P_1$ and $P_2$, respectively. Thus, the players will recieve scores $M_{<1,2>}=3$ and $M_{<2,1>}=3$, respectively.

\begin{figure}[h]
  \caption{Example $2\times2$ payoff matrix with sample moves and resulting scores.}
	\label{fig:1}
	\begin{align*}
	&\text{Payoff Matrix} &(P_1&,P_2) &\text{Payoffs}\\
  &M=
  \begin{bmatrix}
	  2 & 1\\
	  3 & 0
  \end{bmatrix}
  &(1&,2)
  &(1,3)
  \end{align*}
\end{figure}

@@

\subsection{Prisoner's Dilemma}

\begin{figure}[h]
  \caption{Result graphs from test matrix 1.}
	\label{fig:1607068848885-graphs}
	\centering\includegraphics[width=4in]{1607068848885-completed/scores.png}
\end{figure}

@@

\begin{figure}[h]
  \caption{Test cases for first dataset with memories and probability information.}
	\label{fig:1607068848885-cases}
	\[\begin{array}{l r|l}
		&\text{Memory Input} & \text{Move Probabilities} \\
		\hline
		1&{[1, 1, 1, 1, 1, 1]} & {[0.937, 0.063]} \\
		2&{[0, 0, 0, 0, 0, 0]} & {[0.015, 0.985]} \\
		3&{[1, 1, 1, 1, 1, 2]} & {[0.999, 0.001]} \\
		4&{[1, 2, 1, 2, 1, 2]} & {[1.000, 0.000]} \\
		5&{[1, 1, 1, 1, 2, 1]} & {[0.104, 0.896]} \\
		6&{[2, 2, 2, 2, 2, 2]} & {[0.048, 0.952]} \\
	\end{array}\]
\end{figure}
